Value Ordering, Discrepancies, and Restarts in Subgraph Solvers: \\ Some Half-Baked Mucking Around

### 2017-09-27 paper/paper.tex
Fixing

We could try to introduce tiebreaking mechanisms to further refine this heuristic. However, given
the extreme cost of making an incorrect branching choice early on in search, we believe it is more
fruitful to investigate alternatives to simple backtracking (depth-first) search. This paper
evaluates two such approaches: discrepancy search (which perform poorly), and restarts (which are
extremely beneficial). To make restarts work, we introduce a new value-ordering heuristic, which is
nearly the same as ``highest degree first'' except with small amounts of heavily biased randomness.
The effects of the changes we propose are shown in the top plot of \cref{figure:scatter}: we can
make a state-of-the-art algorithm's perform much better on a large number of satisfiable instances,
without substantially degrading its performance on unsatisfiable or the remaining satisfiable
instances.

@@

?? Started with the Glasgow algorithm, removed parts which did not contribute hugely to speedups,
and ended up with a simpler algorithm that performs as well in practice. In particular, large
graphs, no ILF, and not doing supplemental graphs of length 3. This is \cref{algorithm:sip},
ignoring the shaded parts, which are introduced in the context of restarts.

@@

\caption{Subgraph isomorphism. Shaded code is to be ignored for the non-restarting algorithm.}

>>>>

We could try to introduce tiebreaking mechanisms to further refine this heuristic. However, given
the extreme cost of making an incorrect branching choice early on in search, we believe it is more
fruitful to investigate alternatives to simple backtracking (depth-first) search. This paper
evaluates two such approaches: discrepancy search (which perform poorly), and restarts (which are
extremely beneficial). To make restarts work, we introduce a new value-ordering heuristic, which is
nearly the same as ``highest degree first'' except with small amounts of heavily biased randomness.
The effects of the changes we propose are shown in the top plot of \cref{figure:scatter}: we can
make a state-of-the-art algorithm perform much better on a large number of satisfiable instances,
without substantially degrading its performance on unsatisfiable or the remaining satisfiable
instances.

@@

?? Started with the Glasgow algorithm, removed parts which did not contribute hugely to speedups,
and ended up with a simpler algorithm that performs as well in practice. In particular, because we
will be working with reasonably large target graphs, no ILF, and not doing supplemental graphs of
length 3. This is \cref{algorithm:sip}, ignoring the shaded parts, which are introduced in the
context of restarts.

@@

\caption{Non-induced subgraph isomorphism. Shaded code is added for the restarting variant.}
